Insert the article title here

### 2018-08-08 writeup/manuscript.tex
More work on the intro

In the current study, we focus on one source of individual differences in visual search: strategy. By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display. Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \cite{}.   This is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation. Perhaps surprisingly, previous literature has shown that both ideal observer \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise. These apparent contradictory results could potentially explained by large individual differences. Search strategy can also vary in how systematic is it. For example it is common to see top-to-bottom and left-to-right scanning behaviour in scan-paths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.

@@

In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters. The Adaptive Choice Visual Search (ACVS) paradigm  \cite{irons-leber2016} examined strategies in the use of feature-based attention\cite{irons-leber2016,irons-leber2018} \ldots. Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to nearly optimal), and how often they changed search features. Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between the optimal  \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies. We found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times. Examples of the stimuli are given in Figure \ref{fig:exampleStimuli}.

@@

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.

>>>>

In the current study, we focus on one source of individual differences in visual search: strategy. By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display. Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy\cite{gilchrist2006}, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \cite{wolfe2015}. Perhaps surprisingly, previous literature has shown that both ideal observer \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required to locate a target in noise. These apparent contradictory results could potentially explained by large individual differences \cite{nowakowska2017}.

@@

In our own work, we have previously shown that there are large differences between individuals in terms of the search strategies used to find a target among distracters. The Adaptive Choice Visual Search (ACVS) paradigm\cite{irons-leber2016} was used to examine strategies in the use of feature-based attention. [See below and supplementary materials for a description of this paradigm.] Participants varied substantially along two key dimensions: how frequently they used the more effective target feature to search (varying from chance performance to near optimal), and how often they changed search features. Further work has shown that these differences are stable over time (between one and ten days) with test-retest correlations of around $r = 0.8$\cite{irons-leber2018}.

Using a different paradigm\cite{nowakowsak2017}, we aimed to discriminate between optimal\cite{najemnik-geisler2008} and stochastic \cite{clarke2016} search strategies in a simple visual search task involving arrays of line segments (see Figure \ref{fig:exampleStimuli}). The line segments were arranged such that those on one side of the display all had a very similar orientation, while those on the other side had higher variance. This was done so that if the target appeared on the homogeneous side, it would be highly salient. Trials in which the target appeared on the heterogeneous side of the display would be much harder. With these stimuli, the optimal eye movement strategy is to only search the heterogeneous half of the stimulus, as targets on the homogeneous side can be detected with peripheral vision. We found that while some participants initially searched the displays near optimally, others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. Furthermore, the degree to which they made saccades in line with the optimal search strategy was strongly correlated with their reaction times.

@@

Another example of differences in search strategy comes from the foraging literature \cite{kristjansson2014,johannesson2016}. In this context, foraging is a visual search task in which there are multiple targets on each trial. Participants were asked to search through a set of items from four categories, two of which were classed as targets. In the conjunction condition (i.e. searching for red-horizontal and green-vertical line segments among red-vertical and green-horizontal distracters), most observers searched in runs of one target category or another. This strategy has previously been observers in animal foraging literature \cite{dawkins1971}. However, a sub-set of observers, termed ``super-searchers'' showed no switch cost.
